Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-09 paper_jasa.tex
new figure to verify pvalue pick
experiment2 p-value data and plot added

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.6}{\includegraphics{p_val_rank_counts.pdf}}
       \caption{Rank of p-values in a lineup of size 20 and the number of subjects choosing that plot in the lineup of experiment 1 with raw data (nothing is dropped). This indicates that most of the subjects pick the plot with minimum p-value (rank 1). There are subjects choosing the lineups with highest p-value(rank 20) but we can attribute this behavior to the type-I error. Can we?}
       \label{fig:P-val_rank}
\end{figure*}

>>>>

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.6}{\includegraphics{p_val_rank_counts.pdf}}
       \scalebox{0.6}{\includegraphics{p_val_rank_counts2.pdf}}
       \caption{Rank of p-values in a lineup of size 20 and the number of subjects choosing that plot in the lineup of experiment 1 and 2 (bottom) with raw data (nothing is dropped). This indicates that most of the subjects pick the plot with minimum p-value (rank 1). There are subjects choosing the lineups with highest p-value(rank 20) but we can attribute this behavior to the type-I error. Can we?}
       \label{fig:P-val_rank}
\end{figure*}

\green{I think it is very interesting to look at the individual lineups by beta, and other parameters, and we can see the tendency to pick the lowest $p$-value. Figure \ref{fig:P-val_log}.}

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.6}{\includegraphics{p_val_log_counts.pdf}}
       \caption{Frequency of plot picks by log$_10$ $p$-value in individual lineups}
       \label{fig:P-val_log}
\end{figure*}
